Functory: A Distributed Computing Library \\ for Objective Caml \thanks{This research was partly supported by the French national project U3CAT (\emph{Unification of Critical C Code Analysis Techniques}, ANR-08-SEGI-021).}

### 2011-09-29 doc/tfp_2011_final/main.tex
*** empty log message ***

\author{Jean-Christophe Filli\^{a}tre \and K. Kalyanasundaram}
\authorrunning{J.-C. Filli\^atre \and K. Kalyanasundaram}

\institute{
  CNRS, LRI, Univ Paris-Sud 11, Orsay F-91405\\
  INRIA Saclay - \^{I}le-de-France, ProVal, Orsay, F-91893 \\
   \email{filliatr@lri.fr, kalyan.krishnamani@inria.fr}}

@@

%\vfill\pagebreak
\bibliographystyle{plain}
\bibliography{./biblio}

>>>>

\author{Jean-Christophe Filli\^{a}tre and K. Kalyanasundaram}
\authorrunning{J.-C. Filli\^atre \and K. Kalyanasundaram}

\institute{CNRS, LRI, Univ Paris-Sud 11, Orsay F-91405\\
  INRIA Saclay - \^{I}le-de-France, ProVal, Orsay, F-91893 \\
   \email{filliatr@lri.fr, kalyan.krishnamani@inria.fr}}

@@

%\vfill\pagebreak
%\bibliographystyle{plain}
%\bibliography{./biblio}
\begin{thebibliography}{10}

\bibitem{camlP3l}
{CamlP3l}.
\newblock \url{http://camlp3l.inria.fr/}.

\bibitem{plasma}
{Plasma}.
\newblock \url{http://plasma.camlcity.org/plasma}.

\bibitem{erlang}
{The Erlang Programming Language}.
\newblock \url{http://www.erlang.org/}.

\bibitem{GMP}
{The GNU Multiple Precision Arithmetic Library}.
\newblock \url{http://gmplib.org/}.

\bibitem{PASCO}
{Parallel Symbolic Computation 2010 (PASCO)}, 2010.
\newblock \url{http://pasco2010.imag.fr/}.

\bibitem{mapreduce}
Jeffrey Dean and Sanjay Ghemawat.
\newblock {MapReduce: Simplified Data Processing on Large Clusters}.
\newblock In {\em OSDI}, pages 137--150, 2004.

\bibitem{filliatre07cav}
Jean-Christophe Filli\^atre and Claude March\'e.
\newblock {The {Why/Krakatoa/Caduceus} Platform for Deductive Program
  Verification}.
\newblock In Werner Damm and Holger Hermanns, editors, {\em 19th International
  Conference on Computer Aided Verification}, volume 4590 of {\em Lecture Notes
  in Computer Science}, pages 173--177, Berlin, Germany, July 2007. Springer.

\bibitem{iTask}
Jan~Martin Jansen, Rinus Plasmeijer, Pieter Koopman, and Peter Achten.
\newblock {Embedding a Web-based Workflow Management System in a Functional
  Language}.
\newblock In {\em Proceedings of the Tenth Workshop on Language Descriptions,
  Tools and Applications}, LDTA '10, pages 7:1--7:8, New York, NY, USA, 2010.
  ACM.

\bibitem{ocamlMPI}
Xavier Leroy.
\newblock {OCamlMPI: Interface with the MPI Message-passing Interface}.
\newblock \url{http://pauillac.inria.fr/~xleroy/software.html}.

\bibitem{mandel2008}
Louis Mandel and Luc Maranget.
\newblock Programming in {JoCaml} (tool demonstration).
\newblock In {\em 17th European Symposium on Programming ({ESOP 2008})}, pages
  108--111, Budapest, Hungary, April 2008.

\bibitem{ML5}
Tom Murphy, VII., Karl Crary, and Robert Harper.
\newblock {Type-safe Distributed Programming with ML5}.
\newblock In {\em Proceedings of the 3rd conference on Trustworthy global
  computing}, TGC'07, pages 108--123, Berlin, Heidelberg, 2008.
  Springer-Verlag.

\bibitem{poor-man-mapreduce}
Yoann Padioleau.
\newblock {A Poor Man's MapReduce for OCaml}, 2009.
\newblock \url{http://www.padator.org/ocaml/mapreduce.pdf}.

\bibitem{GdH}
Robert~F. Pointon, Philip~W. Trinder, and Hans-Wolfgang Loidl.
\newblock {The Design and Implementation of Glasgow Distributed Haskell}.
\newblock In {\em Selected Papers from the 12th International Workshop on
  Implementation of Functional Languages}, IFL '00, pages 53--70, London, UK,
  2001.

\end{thebibliography}
